---
title: ""
# output:
#   prettydoc::html_pretty:
#     theme: tactile
#     highlight: github
# output: 
#   rmdformats::downcute:
#     self_contained: true
#     thumbnails: true
#     lightbox: true
#     gallery: false
#     highlight: tango
---

<style type = "text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setOptions, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  fig.width = 6,
  warning = FALSE,
  message = FALSE
)
```


```{r}
library(tidyr)
library(lubridate)
library(stringr)
```



## Calgary Traffic Incidents and Construction Detours

<br>

The below map shows the accidents that have been reported in the last 90 minutes. Depending on the severity of the incident, it is possible that the situation has been resolved by the time you travel to the area. Also included are the current construction detours.

Traffic incidents are identified by the red marker, with the car crash icon in them.

Construction detours are identified by the orange markers with the hard hat icon.

Traffic cameras are identified by the blue markers with the video camera icon. You can toggle the camera markers on and off by clicking the layers icon in the top right corner of the map. Clicking on the traffic camera marker will allow you to navigate to the live traffic images.

**Note that the traffic cameras are not enforcement cameras.**

<br>

```{r}
last_update <- Sys.time()
last_update <- format(last_update, tz = "Canada/Mountain", usetz = TRUE)
```

#### Information is updated every 15 minutes. 

<br>

**Last updated at `r last_update`.**

<br><br>



```{r}
# `r now(tzone = "Canada/Mountain")`.**
library(httr2)
library(leaflet)
library(dplyr)
library(lubridate)
library(janitor)
library(fontawesome)

time_frame_min <- 720
current_date_time <- Sys.time()
beginning_time <- current_date_time - lubridate::minutes(time_frame_min)

httr2::req_perform(
        request("https://data.calgary.ca/resource/35ra-9556.csv?$limit=10000000"),
        path = "00_data/yyc_traffic_incidents.csv"
        )

httr2::req_perform(
        request("https://data.calgary.ca/resource/w8zq-79bq.csv?$limit=10000000"),
        path = "00_data/yyc_construction_detours.csv"
        )

httr2::req_perform(
        request("https://data.calgary.ca/resource/k7p9-kppz.csv?$limit=10000000"),
        path = "00_data/yyc_traffic_cams.csv"
        )

file_path <- "00_data/yyc_construction_detours.csv"

raw_construction_detours <- readr::read_csv(file_path)

file_path <- "00_data/yyc_traffic_incidents.csv"

raw_traffic_incidents <- readr::read_csv(file_path)

traffic_cams_raw <- readr::read_csv("00_data/yyc_traffic_cams.csv")

# Data processing ----

# Traffic incidents ----
traffic_incidents <- raw_traffic_incidents |>
    janitor::clean_names() |>
    mutate(
    start_dt = ymd_hms(start_dt,tz = "Canada/Mountain"),
    content = paste(description,incident_info, sep = "<br/>"),
    last_updated = ymd_hms(Sys.time(),tz = "Canada/Mountain"),
    type = "incident"
        ) |>
    filter(start_dt >= beginning_time)

# Construction detours ----
construction_detours <- raw_construction_detours |>
    mutate(
    start_dt = ymd_hms(start_dt,tz = "Canada/Mountain"),
    content = paste(construction_info,description, sep = "<br/>"),
    last_updated = ymd_hms(Sys.time(),tz = "Canada/Mountain"),
    type = "detour"
        ) 

# Traffic cams ----
traffic_cams <- traffic_cams_raw |>
    mutate(
    last_updated = ymd_hms(Sys.time(),tz = "Canada/Mountain"),
    url = stringr::str_extract(camera_url,"(?<=\\()(.*?)(?=\\))"),
    type = "traffic_cam"
        ) |> 
    mutate(
        xy = stringr::str_extract(point,"(?<=\\()(.*?)(?=\\))")
    ) |> 
    tidyr::separate_wider_delim(xy, names = c("longitude", "latitude"), delim = " ") |> 
    select(-camera_url,-point) |> 
    mutate(
        longitude = as.numeric(longitude),
        latitude = as.numeric(latitude),
        # content = paste0("<img src = ", url, " />")
        # content = paste0("a href = ", url, " >", url, "Traffic Cam Live </a>")
        # <a href="https://www.r-project.org/">R Project</a>'
    )

combined_data <- bind_rows(traffic_incidents,construction_detours,traffic_cams)

# glimpse(traffic_incidents)

icons <- awesomeIconList(
  incident = makeAwesomeIcon(text = fa("car-burst"), iconColor = "black", markerColor = "red"),
  detour = makeAwesomeIcon(text = fa("helmet-safety"), iconColor = "black", markerColor = "orange"),
  traffic_cam = makeAwesomeIcon(text = fa("video"), iconColor = "black", markerColor = "blue")
)


```

<center>


```{r, fig.align="center", fig.width=10, fig.height = 6,fig.cap="License: Contains information licensed under the Open Government Licence – City of Calgary."}
# leaflet(combined_data) |>
#  addTiles() |>
#     addAwesomeMarkers(
#         ~longitude, 
#         ~latitude, 
#         popup = ~content,
#         icon = icons[combined_data$type],
#         group = "test"
#         ) |> 
#     addLayersControl(
#     baseGroups = c("test","off"),
#     position = "topright"
#   )
```


```{r, fig.align="center", out.width='100%', fig.height= 8,fig.fullwidth = TRUE,fig.fullheight = TRUE, fig.cap="License: Contains information licensed under the Open Government Licence – City of Calgary."}
leaflet() |>
 addTiles() |>
    addAwesomeMarkers(
        traffic_incidents$longitude, 
        traffic_incidents$latitude, 
        popup = traffic_incidents$content,
        icon = icons[traffic_incidents$type],
        group = "Traffic Incidents"
        ) |> 
    addAwesomeMarkers(
        construction_detours$longitude, 
        construction_detours$latitude, 
        popup = construction_detours$content,
        icon = icons[construction_detours$type],
        group = "Construction Detours"
        ) |>
    addAwesomeMarkers(
        traffic_cams$longitude, 
        traffic_cams$latitude, 
        popup = paste0("<a href = ", traffic_cams$url, " target = _blank>",  "Live Traffic Cam</a>"),
        icon = icons[traffic_cams$type],
        group = "Traffic Cams"
        ) |>
    addLayersControl(
        overlayGroups = c("Traffic Cams", "Traffic Incidents", "Construction Detours"),
        options = layersControlOptions(collapsed = FALSE),
        position = "topright"
  )
```



</center>



<br>

<hr />
<p style="text-align: center;">Created by <a href="https://selica.ca">Selica Analytics</a></p>

<!-- Add icon library -->
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.7.0/css/font-awesome.min.css">

<!-- Add font awesome icons -->
<p style="text-align: center;">
    <a href="https://www.linkedin.com/company/selica-analytics/" class="fa fa-linkedin"></a>
</p>

&nbsp;

<style>

body { background-color: #e0e0db; }
    pre, pre:not([class]) { background-color: red; }

#main .nav-pills > li.active > a,
#main .nav-pills > li.active > a:hover,
#main .nav-pills > li.active > a:focus {
    background-color: #22983B;
}

#main .nav-pills > li > a:hover {
    background-color: #22983B;
}

h1, h2, h3, h4, h5, h6, legend {
    color:#002e4b;
}

#main a {
    background-image: linear-gradient(180deg,#d64a70,#d64a70);
    color: #002e4b;
}

a:hover {
    color: #3d1308;
}
</style>